---
title: "Exercises: Cooking with drake"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)

pkgconfig::set_config_in("drake::strings_in_dots" = "literals", .in = globalenv())

knitr::opts_chunk$set(collapse = TRUE)

library(dplyr)
library(drake)
library(cooking)
```

## Introduction

These exercises introduce the *drake* toy package using functions from *cooking*. In many cases a part of the code is given, and your task is to replace the dots `...` with something meaningful before you can run the code. All exercises on the same topic page build upon each other: If a solution is given, you can assume that objects created in the solution are available to subsequent exercises on the same topic.

If an exercise comes with complete code without dots `...`, it is intended to demonstrate something. Please run the code.

You will only receive feedback to questions, there's no automatic validation for the R code.

The *dplyr*, *drake*, and *cooking* packages are loaded for all exercises:

```r
library(dplyr)
library(drake)
library(cooking)
```

## Plan to buy meat

Add a command that consists of a call to the `buy()` function to your plan. Run the plan and show the output.

```{r drake-buy, exercise=TRUE}
plan <- drake_plan(
  meat = buy("...")
)
```

```{r drake-buy-solution}
plan <- drake_plan(
  meat = buy("meat")
)
```

Display the plan:

```{r drake-buy-view, exercise=TRUE, exercise.setup = "drake-buy-solution"}
plan
str(plan)
```

Execute it:

```{r drake-buy-make, exercise=TRUE, exercise.setup = "drake-buy-solution"}
make(...)
```

```{r drake-buy-make-solution}
make(plan)
```

```{r drake-buy-make-solution-all}
plan <- drake_plan(
  meat = buy("meat")
)
make(plan, verbose = FALSE)
```

Show the contents of the target:

```{r drake-buy-readd, exercise=TRUE, exercise.setup = "drake-buy-make-solution-all"}
readd(..., verbose = FALSE)
```

```{r drake-buy-need-to-remake}
question("What happens if we call make() again?",
  answer("All targets will be up to date", correct = TRUE),
  answer("We need to buy the meat again")
)
```

Verify:

```{r drake-buy-make-again, exercise=TRUE, exercise.setup = "drake-buy-make-solution-all"}
# Without arguments, the most recently used plan will be reused
make()
```

## Plan to chop and fry the meat

Extend the plan with a command that consists of a call to the `chop()` function. Run the plan and show the output.

```{r drake-chop, exercise=TRUE}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = ...(meat)
)
```

```{r drake-chop-solution}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat)
)
```


Execute the `plan` with a call to `make()`:

```{r drake-chop-make, exercise=TRUE, exercise.setup = "drake-chop-solution"}

```

```{r drake-chop-make-solution, eval = FALSE}
make(plan)
```

```{r drake-chop-make-solution-all}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat)
)
make(plan, verbose = FALSE)
```

Show the contents of the newly created target. What's the effect of `verbose = FALSE`?

```{r drake-chop-readd, exercise=TRUE, exercise.setup = "drake-chop-make-solution-all"}
readd(..., verbose = FALSE)
```

Now extend the plan to also fry the chopped meat `with = "oil"`:

```{r drake-fry, exercise=TRUE}
plan <- drake_plan(
  meat = ...,
  chopped_meat = ...,
  fried_meat = ...
)
```

```{r drake-fry-solution}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = "oil")
)
```

```{r drake-fry-solution-all}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = "oil")
)
make(plan, targets = "chopped_meat", verbose = FALSE)
```

Now execute the `plan` and show the fried meat:

```{r drake-fry-make, exercise=TRUE, exercise.setup = "drake-fry-solution-all"}

```

```{r drake-fry-make-solution, eval = FALSE}
make(plan)
readd(fried_meat)
```

Visualize the dependencies in the plan:

```{r drake-fry-vis, exercise = TRUE, exercise.setup = "drake-fry-solution"}
config <- make(plan)
vis_drake_graph(config)
```

## Fry with garlic

For each exercise of this topic we assume that the plan from last topic has been created and executed:

```r
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = "oil")
)
make(plan, verbose = FALSE)
```

```{r setup-garlic, eval = FALSE, echo = TRUE}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = "oil")
)
make(plan, verbose = FALSE)
```

Adapt the plan to fry `with = c("oil", "garlic")`:

```{r drake-garlic-fry, exercise=TRUE, exercise.setup = "setup-garlic"}
plan <- drake_plan(
  ...
)
```

```{r drake-garlic-fry-solution}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(meat, with = c("oil", "garlic"))
)
```

```{r drake-garlic-fry-solution-all}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = "oil")
)
make(plan, verbose = FALSE)
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
```

```{r drake-garlic-targets-change}
question("What do we get if we query the value of the `fried_meat` target now?",
  answer("Meat fried with oil", correct = TRUE),
  answer("Meat fried with oil and garlic",
         message = "No, *drake* is not yet aware of the new plan, and we haven't run it yet.")
)
```

Double-check this:

```{r drake-garlic-new-plan-without-make, exercise=TRUE, exercise.setup = "drake-garlic-fry-solution-all"}
readd(fried_meat)
```

The visualization also shows which targets are up to date.

```{r drake-garlic-new-plan-without-make-vis, exercise=TRUE, exercise.setup = "drake-garlic-fry-solution-all"}
config <- drake_config(plan)
vis_drake_graph(config)
```

Use `outdated()` to list the outdated targets.

```{r drake-garlic-new-plan-without-make-outdated, exercise=TRUE, exercise.setup = "drake-garlic-fry-solution-all"}
config <- drake_config(plan)
outdated(...)
```



```{r drake-garlic-targets-outdated}
question("Why are the `meat` and `chopped_meat` targets not listed as outdated targets?",
  answer("Because the code and the inputs that define these targets haven't changed.", correct = TRUE),
  answer("Because they are listed before `fried_meat` in the plan data frame.",
         message = "No, the order of rows in the plan data frame doesn't matter, *drake* will only consider the dependency relationship.")
)
```


```{r drake-garlic-need-to-remake-quiz}
question(
  "How do we update the `fried_meat` target? Please mark all correct answers.",
  
  answer("`make()`",
         message = "Running `make()` won't change anything, because we haven't told *drake* about our new plan yet."),

  answer("`make(); make()`",
         message = "Even running `make()` twice won't change anything, because we haven't told *drake* about our new plan yet."),

  answer("`make(plan)`",
         correct = TRUE),

  answer("`make(plan, targets = \"meat\")`",
         message = "The `meat` doesn't need updating."),

  answer("`make(plan, targets = \"chopped_meat\")`",
         message = "The `chopped_meat` doesn't need updating."),

  answer("`make(plan, targets = \"fried_meat\")`",
         correct = TRUE)
)
```

Update all targets now, and double-check that they are up to date:

```{r drake-garlic-make-again, exercise=TRUE, exercise.setup = "drake-garlic-fry-solution-all"}

```

```{r drake-garlic-make-again-solution, eval = FALSE}
make(plan)
readd(meat)
readd(chopped_meat)
readd(fried_meat)
```

## Go to the butcher shop instead

For each exercise of this topic we assume that the plan from last topic has been created and executed:

```r
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
make(plan, verbose = FALSE)
```

```{r setup-butcher, eval = FALSE, echo = TRUE}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
make(plan, verbose = FALSE)
```

Adapt the plan to buy meat `from = "the butcher shop"` instead of the supermarket.

```{r drake-butcher-buy, exercise=TRUE, exercise.setup = "setup-butcher"}
plan <- drake_plan(
  ...
)
```

```{r drake-butcher-buy-solution}
plan <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
```

```{r drake-butcher-buy-solution-all}
plan <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
make(plan, verbose = FALSE)
plan <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)
```

```{r drake-butcher-targets-change}
question("What do we get if we query the value of the `meat` target now?",
  answer("Meat from the butcher shop",
         message = "No, *drake* is not yet aware of the new plan, and we haven't run it yet."),
  answer("Meat from the supermarket", correct = TRUE)
)
```

```{r drake-butcher-targets-change-chopped}
question("What do we get if we query the value of the `chopped_meat` target now?",
  answer("Chopped meat made of meat from the butcher shop",
         message = "No, *drake* is not yet aware of the new plan, and we haven't run it yet."),
  answer("Raw meat from the supermarket",
         message = "No, `chopped_meat` still has chopped meat."),
  answer("Chopped meat made of meat from the supermarket", correct = TRUE)
)
```

Double-check this:

```{r drake-butcher-new-plan-without-make, exercise=TRUE, exercise.setup = "drake-butcher-buy-solution-all"}
readd(meat)
readd(chopped_meat)
```

```{r drake-butcher-need-to-remake-quiz}
question(
  "How do we update all targets? Please mark all correct answers.",
  
  answer("`make()`",
         message = "Running `make()` won't change anything, because we haven't told *drake* about our new plan yet."),

  answer("`make(); make()`",
         message = "Even running `make()` twice won't change anything, because we haven't told *drake* about our new plan yet."),

  answer("`make(plan)`",
         correct = TRUE),

  answer("`make(plan, targets = \"meat\")`",
         message = "Updating the `meat` target only will not automatically update the `chopped_meat` and `fried_meat` targets."),

  answer("`make(plan, targets = \"chopped_meat\")`",
         message = "Updating the `chopped_meat` target only will not automatically update the `fried_meat` target."),

  answer("`make(plan, targets = \"fried_meat\")`",
         correct = TRUE)
)
```

Update all targets now, and double-check that they are up to date:

```{r drake-butcher-make-again, exercise=TRUE, exercise.setup = "drake-butcher-buy-solution-all"}

```

```{r drake-butcher-make-again-solution, eval = FALSE}
make(plan)
readd(meat)
readd(chopped_meat)
readd(fried_meat)
```

```{r drake-butcher-targets-quiz}
question(
  "Which of the following statements is correct?",
  
  answer("We need to restart the R session befor we can update the `chopped_meat` target.",
         message = "Restarting the R session is not necessary, but doesn't hurt either, because we have recorded the work to be done in a plan."),
  
  answer("The `chopped_meat` target cannot be updated before the `meat` target is updated.",
         correct = TRUE),
  
  answer("The `chopped_meat` target cannot be updated before the `fried_meat` target is updated.",
         message = "No, because `chopped_meat` is not a dependency to `fried_meat` (only the other way round)."),
  
  answer("We need to update the `meat` target manually before we can update the `chopped_meat` target.",
         message = "No, *drake* will automatically update the `meat` target before starting to work on `chopped_meat`."),

  answer("To update the `meat` target, we need to reload the *drake* package.",
         message = "Reloading the *drake* package doesn't have any side effects."),

  answer("Running `make(plan, targets = \"meat\"); make()` will update the `chopped_meat` target.",
         correct = TRUE),

  answer("If we run the code `meat = buy(\"meat\", from = \"the butcher shop\")`, the `meat` target will be updated.",
         message = "This will update the variable `meat`, but *not* the target."),

  answer("If we run the code `meat = buy(\"tofu\"); make()`, we can trick *drake* into building `chopped_meat` and `fried_meat` with the wrong ingredients.",
         message = "No, `make()` will remove the `meat` object we created.")
)
```

## Prepare vegetables

We don't assume any plans for the exercises in this topic.

Create a plan solely to prepare carrots: Buy them and `peel()` them. Run the plan.

```{r drake-vegetables-carrots, exercise=TRUE}
plan_carrots <- drake_plan(
  carrots = ...,
  peeled_carrots = ...
)

...
```

```{r drake-vegetables-carrots-solution}
plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

make(plan_carrots)
```

Create another plan solely to prepare potatoes: Buy them, peel them, and then `cook()` them. Implement a function `prepare_potatoes()` to both peel and cook the potatoes.

```{r drake-vegetables-potatoes, exercise=TRUE}
prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- ...(peeled_potatoes)
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  ...,
  cooked_potatoes = ...
)

...
```

```{r drake-vegetables-potatoes-solution}
prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes)
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

make(plan_potatoes)
```


```{r drake-vegetables-potatoes-solution-all}
prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes)
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

make(plan_potatoes, verbose = FALSE)
```

We forgot to add salt when cooking the potatoes. Add `with = "salt"` to the `cook()` call in the `prepare_potatoes()` function. Does this invalidate the `cooked_potatoes` target? What happens if you call `make()`? Show the value of the `cooked_potatoes` target.

```{r drake-vegetables-salt, exercise=TRUE, exercise.setup = "drake-vegetables-potatoes-solution-all"}
prepare_potatoes <- ...

message("*** Showing outdated targets")
config <- drake_config(verbose = FALSE)
outdated(...)

message("*** Updating targets")
make()

message("*** Displaying target")
...
```

```{r drake-vegetables-salt-solution}
prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

message("*** Showing outdated targets")
config <- drake_config(verbose = FALSE)
outdated(config)

message("*** Updating targets")
make()

message("*** Displaying target")
readd(cooked_potatoes)
```


```{r drake-vegetables-salt-solution-all}
prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

make(plan_potatoes, verbose = FALSE)
```

Verify the visualization to see why the `cooked_potatoes` target is updated when we change the definition of `prepared_potatoes()`.

```{r drake-vegetables-salt-vis, exercise=TRUE, exercise.setup = "drake-vegetables-salt-solution-all"}
vis_drake_graph(drake_config())
```

```{r drake-vegetables-functions-quiz}
question(
  "Why does `make()` update the `cooked_potatoes` target?",
  
  answer("Because we changed the text of the command used to create this target.",
         message = "We didn't in fact change the text of the command."),
  
  answer("Because we changed a function used by the command that creates this target.",
         correct = TRUE),
  
  answer("Because `make()` always rebuilds all targets.",
         message = "`make()` will only update the outdated targets."),
  
  answer("Because `make()` always rebuilds all targets if the command calls functions defined by the user.",
         message = "`make()` will only update the outdated targets. It will even analyze the functions defined by the user, as well as any other functions it uses.")
)
```

## Combine the ragout

In the last two topics we created three plans (and one function), which will be available for each exercise in this topic:

```r
plan_meat <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)
```

```{r setup-combine, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)
```

To create a ragout from the three components `fried_meat`, `peeled_carrots`, and `cooked_potatoes`, we need another step. Implement it in a new plan using the `combine()` function:

```{r drake-combine-ragout, exercise=TRUE, exercise.setup = "setup-combine"}
plan_ragout <- ...
```

```{r drake-combine-ragout-hint, eval = FALSE}
plan_ragout <- drake_plan(
  ragout = combine(fried_meat, ...)
)
```

```{r drake-combine-ragout-solution, eval = FALSE}
plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)
```

```{r drake-combine-ragout-solution-all, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)
```

For safe operation and optimal reproducibility, we need one single plan. How do we combine the four plans? (Hint: Remember the plans are data frames.)

```{r drake-combine-plans, exercise=TRUE, exercise.setup = "drake-combine-ragout-solution-all"}

```

```{r drake-combine-plans-hint-1, eval = FALSE}
plan <- bind_rows(...)
```

```{r drake-combine-plans-hint-2, eval = FALSE}
plan <- bind_rows(plan_meat, ...)
```

```{r drake-combine-plans-solution, eval = FALSE}
plan <- bind_rows(plan_meat, plan_carrots, plan_potatoes, plan_ragout)
```

```{r drake-combine-plans-solution-all, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)

plan <- bind_rows(plan_meat, plan_carrots, plan_potatoes, plan_ragout)
```

View the dependency graph:

```{r drake-combine-view, exercise=TRUE, exercise.setup = "drake-combine-plans-solution-all"}

```

```{r drake-combine-view-hint, eval = FALSE}
config <- ...
vis_...(...)
```

Run the plan:

```{r drake-combine-run, exercise=TRUE, exercise.setup = "drake-combine-plans-solution-all"}

```

```{r drake-combine-run-solution, eval = FALSE}
make(plan)
```

```{r drake-combine-run-solution-all, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)

plan <- bind_rows(plan_meat, plan_carrots, plan_potatoes, plan_ragout)

make(plan, verbose = FALSE)
```

Enjoy!

```{r drake-combine-enjoy, exercise=TRUE, exercise.setup = "drake-combine-run-solution-all"}
readd(ragout)
```



## Combine the ragout the wrong way

The four plans and one function from the last topic will be available for each exercise in this topic:

```r
plan_meat <- drake_plan(
  meat = buy("meat"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)
```

```{r setup-uncombine, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)
```

Try creating the ragout by just running `plan_ragout`:

```{r drake-uncombine-make-incomplete, exercise=TRUE, exercise.setup = "setup-uncombine"}
make(plan_ragout)
```

```{r drake-uncombine-make-incomplete-all, eval = FALSE}
plan_meat <- drake_plan(
  meat = buy("meat", from = "the butcher shop"),
  chopped_meat = chop(meat),
  fried_meat = fry(chopped_meat, with = c("oil", "garlic"))
)

plan_carrots <- drake_plan(
  carrots = buy("carrots"),
  peeled_carrots = peel(carrots)
)

prepare_potatoes <- function(potatoes) {
  peeled_potatoes <- peel(potatoes)
  cooked_potatoes <- cook(peeled_potatoes, with = "salt")
  cooked_potatoes
}

plan_potatoes <- drake_plan(
  potatoes = buy("potatoes"),
  cooked_potatoes = prepare_potatoes(potatoes)
)

plan_ragout <- drake_plan(
  ragout = combine(fried_meat, peeled_carrots, cooked_potatoes)
)

try(make(plan_ragout, verbose = FALSE))
```

Visualize the failed run:

```{r drake-uncombine-make-vis, exercise=TRUE, exercise.setup = "drake-uncombine-make-incomplete-all"}

```

```{r drake-uncombine-make-vis-hint, eval = FALSE}
config <- ...
...(...)
```

What went wrong with the `ragout`?

```{r drake-uncombine-make-diagnose, exercise=TRUE, exercise.setup = "drake-uncombine-make-incomplete-all"}
diagnose(...)
```

```{r drake-uncombine-functions-quiz}
question(
  "Why does `make()` fail?",
  
  answer("Because the plan doesn't contain the `fried_meat`, `peeled_carrots` and `cooked_potatoes` targets.",
         correct = TRUE),

  answer("Because we don't have variables named `fried_meat`, `peeled_carrots` and `cooked_potatoes` in our global environment.",
         message = "Beware! We could perhaps run such a plan, but then `fried_meat`, `peeled_carrots` and `cooked_potatoes` would not be under the control of *drake*.")
)
```

Try running all plans in sequence, and visualizing the run. Do you see the problem?

```{r drake-uncombine-make-sequence, exercise=TRUE, exercise.setup = "setup-uncombine"}
make(plan_meat)
make(plan_carrots)
make(plan_potatoes)
config <- make(plan_ragout)
vis_drake_graph(config)
```

```{r drake-uncombine-sequence-quiz}
question(
  "Why does `make()` succeed?",
  
  answer("Because running plans in sequence effectively combines them.",
         message = "We need to create one single plan that contains all targets for optimal reproducibility."),
  
  answer("Because the first three `make()` runs have created objects named `fried_meat`, `peeled_carrots` and `cooked_potatoes` in our global environment as a side effect.",
         correct = TRUE)
)
```
