---
title: "Exercises: Cooking"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)

library(cooking)
```

## Introduction

These exercises introduce the *cooking* toy package. In many cases a part of the code is given, and your task is to replace the dots `...` with something meaningful before you can run the code. All exercises are self-contained.

You will only receive feedback to questions, there's no automatic validation for the R code.

The *cooking* package is loaded for all exercises:

```r
library(cooking)
```


## Buy meat

Use the `buy()` function to buy meat.

```{r buy, exercise=TRUE}
buy("...")
```

What changes if you pass the `from` argument?

```{r buy-from, exercise=TRUE}
buy(..., from = "the butcher's")
```

Can you store the meat for later use?

```{r buy-store, exercise=TRUE}
meat <- ...
meat
```

```{r buy-store-solution}
meat <- buy("meat")
meat
```

## Chop meat

We have our raw meat ready (in the `meat` variable).

```{r prepare-chop}
meat <- buy("meat")
```

Double-check by accessing this variable.

```{r chop-test, exercise=TRUE, exercise.setup = "prepare-chop"}
meat
```

Now let's chop it, use the `chop()` function.

```{r chop-meat, exercise=TRUE, exercise.setup = "prepare-chop"}
chop(...)
```

Store the chopped meat in a variable for later access.

```{r chop-meat-store, exercise=TRUE, exercise.setup = "prepare-chop"}
... <- ...
```

```{r chop-meat-store-solution}
chopped_meat <- chop(meat)
chopped_meat
```

## Fry meat

We have chopped the meat and stored it in the `chopped_meat` variable.

```{r prepare-fry}
chopped_meat <- chop(buy("meat"))
```

Double-check by accessing this variable.

```{r fry-test, exercise=TRUE, exercise.setup = "prepare-fry"}
chopped_meat
```

Fry the chopped meat with oil, using the `fry()` function.

```{r fry-meat, exercise=TRUE, exercise.setup = "prepare-fry"}
...(..., with = "oil")
```

Let's add garlic, too.

```{r fry-meat-garlic, exercise=TRUE, exercise.setup = "prepare-fry"}
...(..., ...)
```

<div id="fry-meat-garlic-hint">
**Hint**: Use `with = c("oil", "garlic")`.
</div>

Store the fried meat in a variable for later access.

```{r fry-meat-store, exercise=TRUE, exercise.setup = "prepare-fry"}

```

```{r fry-meat-store-solution}
fried_meat <- fry(chopped_meat, with = "oil")
fried_meat
```

## The ragout

The fried meat is available in the `fried_meat` variable.

```{r prepare-combine}
fried_meat <- fry(chop(buy("meat")), with = "oil")
```

Double-check by accessing this variable.

```{r combine-test, exercise=TRUE, exercise.setup = "prepare-combine"}
fried_meat
```

Combine the fried meat with vegetables (using `combine()`) to finish the ragout.

```{r combine-meat, exercise=TRUE, exercise.setup = "prepare-combine"}

```

Put the ragout aside into a variable for later access.

```{r ragout-store, exercise=TRUE, exercise.setup = "prepare-combine"}

```

```{r ragout-store-solution}
ragout <- combine(fried_meat, with = "vegetables")
ragout
```

## The salad

We need to learn how to slice and dice first. Our new `slice()` function is supposed to cut its ingredient to slices:

```{r slice, exercise=TRUE, exercise.setup = "prepare-combine"}
slice <- make_cooking("...")
slice("cucumber")
```

We also need a `dice()` function.

```{r dice, exercise=TRUE, exercise.setup = "prepare-combine"}
...
dice("tomato")
```

## Dinner's ready!

We have our `ragout`, and our `slice()` and `dice()` functions

```{r prepare-serve}
ragout <- combine(fry(chop(buy("meat")), with = "oil"), with = "vegetables")
slice <- make_cooking("sliced")
dice <- make_cooking("diced")
```

Double-check:

```{r serve-test, exercise=TRUE, exercise.setup = "prepare-serve"}
ragout
slice("tomato")
dice("cucumber")
```

Now serve a meal that consists of the ragout and a dressed salad with ingredients of your choice. Add other components if you like: bread (with butter?), a soup maybe, dessert, ...

```{r serve, exercise=TRUE, exercise.setup = "prepare-serve"}
combine(
  ...,
  ...,
  name = "meal"
)
```

```{r serve-solution}
combine(
  ragout,
  combine(
    slice("cucumber"),
    dice("tomato"),
    "dressing",
    name = "salad"
  ),
  name = "meal"
)
```
